Optimal Task Phasing for End-To-End Latency in Harmonic Systems and Semi-Harmonic Automotive Systems

### 2024-09-26 paper.tex
structure of harmonic section

	\begin{theorem}
		The task phasing presented in Equation~\eqref{eq:phasing} is optimal in minimizing the end-to-end latency for max-harmonic systems.
	\end{theorem}

>>>>

	\begin{theorem}[Optimality]
		If $\Tbb_E$ is max-harmonic, then the task phasing presented in Equation~\eqref{eq:phasing} minimizes the end-to-end latency.
		In particular, the suggested phasing minimizes the end-to-end latency in harmonic systems.
	\end{theorem}
